\TheTitle

### 2016-08-02 linvis.tex
Minor changes
Just making some minor changes and grammar fixes.

In this paper, we propose the merge-tree view, a simplified transformation
of the DAG of the Linux git repository that shows the way in which commits
are merged into the master branch of Linux. Using the merge-tree view we
build \tool, a tool that is designed to allow users to explore how commits
are merged into the Linux kernel.

@@

Between 50k and 70k commits are added to the Linux kernel per version requiring
maintainers of older versions of the Linux kernel to sift through thousands of
commits and merges with tools that are unable to filter and effectively visualize
projects at the scale of the kernel. Older versions of the kernel are used in
embedded systems and mobile phones; for security purposes, performance needs, and
changing hardware requirements, maintainers must be able to understand the changes
being made in the current version of the kernel in order to produce the necessary
patches for the older versions of the kernel. Tools like Gitk use a directed acyclic
graph (DAG) model of the repository, showing all commits and merges in chronological
order by when the commit was authored, not by when it arrived in the official Linux
repository.

@@

These methods and visualizations are implemented in a web-based tool called
\tool\footnote{\tool is currently available at \url{http://li.turingmachine.org}}.
Our visualizations and tool provide information about the location of any given
commit in its respective merge-tree, the files edited, the modules edited, and the
commit message for a given commit or merge. \tool allows users to apply various
filters, including the release version, along with a keyword or phrase from the log
preview, the name of the author, or the commit ID. The user can request all merges
made by Linus that contain a commit or inner merge that matches the search query, or
just the commits and merges that match the query.

@@

A short example: assume the commits represented in Figure~\ref{fig:repoEvents} shows
the sequence of events in a repository. In this case, commits are performed in
various repositories and branches. The DAG representation of the commits is shown in
Figure~\ref{fig:repoDAG}. Notice that the DAG loses information about the master
branch and the repository that the master branch is part of. The merge-tree view of
this DAG is visible in Figure~\ref{fig:repoTree}. Note that the direction of the
edges of the DAG have been inverted, instead of pointing from the child to the
ancestors, it points from the ancestor to its successors, forming a path to the
master branch. Also note that the DAG has been simplified, showing only a single
edge on the path to master for any commit.

@@

We used this information to evaluate the accuracy of the merge-tree model extracted from the DAG. The method we followed
started with the extraction of the commit history up to July 20, 2016. We computed the merge tree of every commit until
then. Since Linus Torvalds mostly does merging directly into master, we assumed that every merge by him is the root of a
merge-tree. As described above, the log of a commit usually contains the number of commits in the merge the first 20
summaries of commits being merged. We extracted merges by Linus Torvalds using the command \mycode{log --merges --author='Torvalds} and compared
the number of commits in according to the log with the number of commits in the  merge-tree rooted in this commit. We
also used the summaries of the commits found in the merge (not necessarily all---see above) to make sure those 
commits were in their corresponding merge tree. For example, for the merge in Figure~\ref{sampleMerge} we would expect
that the merge tree rooted at \mycode{8cbd84f} contains 24 commits, and the one-line summaries corresponds to commits in
that merge-tree. We also inspected those with differences to make sure they were true errors.
The results can be summarized as follows:

@@

The goal of \tool is to simplify the navigation of the kernel commit information,
specifically focusing on merges. This is done by leveraging the merge-tree view to
inspect how commits are merged on the path to the master repository.

@@

In our visualizations, we leverage the Merge-Tree model described in
Section~\ref{sec:mergetree}. In this model each commit is either already in the
master branch, or is part of a tree which is rooted in the merge that merged it into
the master branch.  Each commit, whether a merge or non-merge, has only one
successor; the root of each tree has none as it was made by Linus Torvalds directly
into the master branch. Non-merge commits contain the metadata for the changes made.
This metadata includes the files changed, the lines added and removed from each
file, the author, the date the commit was merged into the merge that led to being
merged into the kernel, the date the commit was authored, the patch, and the commit
log. Merges contain less metadata, only storing the author of the merge, the log,
the commit date, and the author date, and potentially, changes necessary to address
conflicts during the merge. The details of the model are outlined in
\cite{German2015}.

@@

The first tab displays the full commit log (Figure~\ref{fig:message}). From this, a
user is able to see what they would see had they searched for the commit using Git
log. This doesn't provide additional information to the other tools, but helps to
complete the functionality of \tool. The commit log provides a user with the
information about the content of the commit and who has signed-off on the commit to
ensure that it is of good quality. The message for merges may contain a summary of
the commits being merged.  The information within these messages is highly variable,
and is completely dependent on the author's style. As the user moves toward the
top-level merge, the quality of these messages generally improves.

@@

From a developers point of view, the are two major disadvantages of the DAG model of
Git: a) its edges point backwards, i.e. commits point to their ancestor, not to the
commit that succeeds them on the path to being integrated; and b) the DAG contains
many more edges that are necessary to understand how integration occurred. We
addressed these two issues with the creation of the merge-tree model of the DAG of
Linux. Effectively the merge-tree view recovers the details of how each branch---and the commits they contain---was merged
into the master branch.

In our experience, no other Git repository reaches the level of DAG complexity that
Linux has. In most Git repositories, most merges are not nested---most merges merge
directly into the master repository, and these merges only merge few commits. Even
in these simplified cases, the merge-tree can provide a valuable summary of how
commits are integrated into the master branch, specifically since the time of
integration may be very different from the time the commits were authored.

@@

The biggest challenge is computing the merge-tree of any given repository. It
is likely that our heuristic for computing the merge-tree will not work with other
repositories. The heuristic requires that there are no fast-forward merges into the
master branch of the repository (a majority of repositories), and that there are no
foxtrot merges (this is practice that starts be considered desirable by git users\footnote{See
  \url{http://devblog.nestoria.com/post/98892582763/maintaining-a-consistent-linear-history-for-git} and
  \url{https://developer.atlassian.com/blog/2016/04/stop-foxtrots-now/}}).
We are able to use our heuristic with the Linux kernel because of
the strict integration model imposed by Linus. To validate the results of the
heuristic, we use the continuous mining technique described in \cite{German2015}.
The continuous mining of the repository requiring foresight and planning.

Because \tool leverages the merge-tree model of the kernel, it provides mechanisms
and visualizations that other tools are unable to produce. It gives us the ability to
see how commits are being merged into the kernel, allowing us to better understand
how code is integrated into the kernel.

@@

The merge-tree model used in \tool has many advantages to the DAG model, but there
are two drawbacks. The first drawback is that a server must query the state of the
master repository since time information is not stored by Git in order to properly
construct the merge tree. The second drawback is the need to pre-compute the
merge-tree of the repository.

% Our core model provides advantages to the DAG model used by other tools. We separate
% the commits and merges into sub-trees and focus on a single sub-tree at a time. This
% enables us to filter out commits and merges that do not pertain to the component of
% the kernel that we are interested in, providing a clearer picture of what is
% happening in a given merge. The tree model also enables us to aggregate metadata
% easily. With the addition of the continuous polling of the repository, the model
% provides us with a mechanism of performing date-range queries with meaningful
% results.

@@

\evan{Check the validity of this paragraph}
We use a heuristic method to generate the tree from the repository. The heuristic
requires that the repository does not have fast-forward merges into the master
branch or foxtrot merges, which obfuscate the master branch. In either case, the
heuristic will break and result in a tree that does not accurately represent the
repository. Validation of the results from the heuristic requires continuous mining
of the repository.

While these are significant drawbacks for small projects, large projects will likely
have a more centralized work flow with a master repository where contributions will
eventually land, along with various servers that can watch this master repository
for changes. Given that the importance of clear visualizations of the repository
outweighs the cost of having a server monitor the state of the repository, the
tree-based model appears to provide clean visualizations and explanations of the
changes in the Linux kernel.

>>>>

In this paper, we propose the merge-tree, a simplified transformation
of the DAG of the Linux git repository that shows the way in which commits
are merged into the master branch of Linux. Using the merge-tree, we
build \tool, a tool that is designed to allow users to explore how commits
are merged into the Linux kernel.

@@

Between 50k and 70k commits are added to the Linux kernel per version requiring
maintainers of older versions of the kernel to sift through thousands of
commits and merges with tools that are unable to filter and effectively visualize
projects at the scale of the kernel. Older versions of the kernel are used in
embedded systems and mobile phones; for security purposes, performance needs, and
changing hardware requirements, maintainers must be able to understand the changes
being made in the current version of the kernel in order to produce the necessary
patches for the older versions of the kernel. Tools like Gitk use a directed acyclic
graph (DAG) model of the repository, showing all commits and merges in chronological
order by when the commit was authored, not by when it arrived in the official Linux
repository.

@@

These methods and visualizations are implemented in a web-based tool called
\tool\footnote{\tool is currently available at \url{http://li.turingmachine.org}}.
Our visualizations and tool provide information about the location of any given
commit or merge in its respective merge-tree, the files edited, the modules edited,
and the commit message. \tool allows users to apply various filters, including the
release version, along with a keyword or phrase from the log preview, the name of
the author, or the commit ID. The user can request all merges made by Linus that
contain a commit or inner merge that matches the search query, or just the commits
and merges that match the query.

@@

A short example: assume the commits represented in Figure~\ref{fig:repoEvents} show
the sequence of events in a repository. In this case, commits are performed in
various repositories and branches. The DAG representation of the commits is shown in
Figure~\ref{fig:repoDAG}. Notice that the DAG loses information about the master
branch and the repository that the master branch is part of. The merge-tree view of
this DAG is visible in Figure~\ref{fig:repoTree}. Note that the direction of the
edges of the DAG have been inverted, instead of pointing from the child to the
ancestors, it points from the ancestor to its successors, forming a path to the
master branch. Also note that the DAG has been simplified, showing only a single
edge on the path to master for any commit.

@@

We used this information to evaluate the accuracy of the merge-tree model extracted from the DAG. The method we followed
started with the extraction of the commit history up to July 20, 2016. We computed the merge tree of every commit until
then. Since Linus Torvalds mostly does merging directly into master, we assumed that every merge by him is the root of a
merge-tree. As described above, the log of a merge-commit usually contains the number of commits in the merge the first 20
summaries of commits being merged. We extracted merges by Linus Torvalds using the command \mycode{log --merges --author='Torvalds} and compared
the number of commits according to the log with the number of commits in the  merge-tree rooted in this commit. We
also used the summaries of the commits found in the merge (not necessarily all---see above) to make sure those
commits were in their corresponding merge tree. For example, for the merge in
Figure~\ref{fig:sampleMerge} we would expect
that the merge tree rooted at \mycode{8cbd84f} contains 24 commits, and the one-line summaries corresponds to commits in
that merge-tree. We also inspected those with differences to make sure they were true errors.
The results can be summarized as follows:

@@

The goal of \tool is to simplify the navigation of the kernel commit information,
specifically focusing on merges. This is done by leveraging the merge-tree to
inspect how commits are merged on the path to the master repository.

@@

In our visualizations, we leverage the merge-tree model described in
Section~\ref{sec:mergetree}. In this model each commit is either already in the
master branch, or is part of a tree which is rooted in the merge that merged it into
the master branch.  Each commit, whether a merge or non-merge, has only one
successor; the root of each tree has none as it was made by Linus Torvalds directly
into the master branch. Non-merge commits contain the metadata for the changes made.
This metadata includes the files changed, the lines added and removed from each
file, the author, the date the commit was merged into the merge that led to being
merged into the kernel, the date the commit was authored, the patch, and the commit
log. Merges contain less metadata, only storing the author of the merge, the log,
the commit date, and the author date, and potentially, changes necessary to address
conflicts during the merge. The details of the model are outlined in
\cite{German2015}.

@@

The first tab displays the full commit log (Figure~\ref{fig:message}). From this, a
user is able to see what they would see had they searched for the commit using Git
log. This doesn't provide additional information to the other tools, but helps to
complete the functionality of \tool. The commit log provides a user with the
information about the content of the commit and who has signed-off on the commit to
ensure that it is of good quality. The message for merges may contain a summary of
the commits being merged.  The information within these messages is highly variable,
and is completely dependent on the author's style. As the user moves toward the
root-level merge, the quality of these messages generally improves.

@@

From a developers point of view, the are two major disadvantages of the DAG model of
Git: a) its edges point backwards, i.e. commits point to their ancestor, not to the
commit that succeeds them on the path to being integrated; and b) the DAG contains
many more edges that are necessary to understand how integration occurred. We
addressed these two issues with the creation of the merge-tree model from the DAG of
Linux. Effectively, the merge-tree recovers the details of how each branch---and the commits they contain---was merged
into the master branch.

In our experience, no other Git repository reaches the level of DAG complexity that
Linux has. In most Git repositories, most merges are not nested---most merges merge
directly into the master repository, and these merges only merge a few commits. Even
in these simplified cases, the merge-tree can provide a valuable summary of how
commits are integrated into the master branch, specifically since the time of
integration may be very different from the time the commits were authored.

@@

The biggest challenge is computing the merge-tree of any given repository. It
is likely that our heuristic for computing the merge-tree will not work with other
repositories. The heuristic requires that there are no fast-forward merges into the
master branch of the repository (a majority of repositories), and that there are no
foxtrot merges (a practice that is starting to be considered desirable by git users\footnote{See
  \url{http://devblog.nestoria.com/post/98892582763/maintaining-a-consistent-linear-history-for-git} and
  \url{https://developer.atlassian.com/blog/2016/04/stop-foxtrots-now/}}).
We are able to use our heuristic with the Linux kernel because of
the strict integration model imposed by Linus. To validate the results of the
heuristic, we use the continuous mining technique described in \cite{German2015}.
Continuous mining of the repository requires foresight and planning.

Because \tool leverages the merge-tree model of the kernel, it provides mechanisms
and visualizations that other tools are unable to produce. It gives us the ability to
see how commits are being merged into the master branch, allowing us to better understand
how code is integrated into the kernel.

@@

@@

\evan{Check the validity of this paragraph}
We use a heuristic method to generate the tree from the repository. The heuristic
requires that the repository does not have fast-forward merges into the master
branch or foxtrot merges, which obfuscate the master branch. In either case, the
heuristic will break and result in a tree that does not accurately represent the
repository.

These may pose as significant drawbacks to smaller projects; however, with a proper
merge discipline, the heuristic is able to correctly convert the DAG into a
merge-tree. The importance of clear visualizations in large projects outweighs
the costs of enforcing a clean merge discipline. The tree-based model appears to
have the ability to provide a clean visualization and more detailed explanations of
the changes in the Linux kernel.
